 % Experience
    \cvsection{Experience}
    
    \begin{cventries}
    
      \cventry
        {Software Engineer - Remote}
        {Accelera Digital Group (ADG)}
        {Dubai, UAE}
        {Jan 2026 -- Jun 2026}
        {
          \begin{cvitems}
            \item Develop software demos for customer products
          \end{cvitems}
        }
        
      \cventry
        {Hardware and Software Engineer - On site}
        {Kamitek Solar SMC LTD}
        {Kampala, Uganda}
        {Jul 2025 -- Jan 2026}
        {
          \begin{cvitems}
            \item Developed embedded hardware and firmware for solar-based systems.
            \item Designed test and monitoring systems for automation.
          \end{cvitems}
        }
    
      \cventry
        {Mobile Application Developer - hybrid}
        {Events Gallery Uganda}
        {Kampala, Uganda}
        {Jul 2025 -- Dec 2025}
        {
          \begin{cvitems}
            \item Designed and implemented Android application for event management.
            \item Designed backend architecture for mobile + web application
            \item Created a data management website with different access roles
          \end{cvitems}
        }
    
    
      \cventry
        {Engineering Intern – E-waste Recycling Project}
        {netLabs!UG}
        {Kampala, Uganda}
        {Feb 2023 -- Jul 2025}
        {
          \begin{cvitems}
            \item Part of a team refurbishing e-waste into usable computers for underprivileged communities.
            \item Installed dual-boot (Windows 11 + Ubuntu 22) systems for practical learning.
          \end{cvitems}
        }
    
      \cventry
        {Embedded Systems Intern}
        {IoT-ra (Internet of Things - Research \& Applications) Lab}
        {Kampala, Uganda}
        {Mar 2024 -- Apr 2025}
        {
          \begin{cvitems}
            \item Developed Firmware for power managment module.
            \item Designed 3d models and operated 3d printer.
            \item Field testing and debugging of hive prototypesS
          \end{cvitems}
        }
    
      \cventry
        {Back End Developer}
        {Accelera Digital Group (ADG)}
        {Kampala, Uganda}
        {Dec 2024 -- Feb 2025}
        {
          \begin{cvitems}
            \item Developed Docker Compose environments integrated with GCP services.
          \end{cvitems}
        }
    
      \cventry
        {Engineering Intern – Software Development \& Data Analysis}
        {Green Hub East Africa Ltd}
        {Kampala, Uganda}
        {Jan 2024 -- Sep 2024}
        {
          \begin{cvitems}
            \item Supported data analysis, database design, and automation for E-mobility.
            \item Built company site on existing Infra with GoDaddy
            \item Assisted in development of a battery-swapping infrastructure.
          \end{cvitems}
        }
    
      \cventry
        {Project Assistant – Green Hub Kampala (E-Mobility)}
        {Access2Innovation}
        {Aalborg, Denmark}
        {Jun 2024 -- Aug 2024}
        {
          \begin{cvitems}
            \item Supported international collaboration on sustainable E-Mobility solutions.
          \end{cvitems}
        }
    
      \cventry
        {Undergraduate Internship}
        {Marconi Research and Innovations Laboratory}
        {Kampala, Uganda}
        {Feb 2024 -- Aug 2024}
        {
          \begin{cvitems}
            \item Trained a Runyankore natural voice language model for smart agriculture.
            \item Achieved a 50\% model acuracy
          \end{cvitems}
        }
    
      \cventry
        {Internship Coordinator}
        {Dojo Hub (SMC) Ltd}
        {Kampala, Uganda}
        {Jun 2023 -- Aug 2023}
        {
          \begin{cvitems}
            \item Managed logistics, training schedules, and reporting for the internship program.
          \end{cvitems}
        }
      
    \end{cventries}